---
params:
  watermark: false
title: "Project Title"
shorttitle: "Short Project Title"
subtitle: "Type of Report"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
knit: rmarkdown::render
# knit: wjake::knit_with_contract
site: "bookdown::bookdown_site"
author:
  name: W. Jake Thompson, Ph.D.
  return-address: 12261 S Crest Drive \bullet\ Olathe, KS 66061
  return-email: \nolinkurl{wjakethompson@gmail.com}
  return-phone: (785) 643-9244
  fee: 200
  hourly: true
  agree_date: "2015-07-17"
  complete_date: "2016-09-04"
recepient:
  name: W. Jake Thompson, Ph.D.
  position: Senior Psychometrician
  organization: Accessible Teaching, Learning, and Assessment Systems
  address1: Joseph R. Pearson Hall
  address2: 1122 West Campus Road, Room 437
  address3: Lawrence, KS 66045
  email: jakethompson\@ku.edu
output: wjake::consulting_report
bibliography: ["bib/refs.bib", "bib/packages.bib"]
biblio-style: apa
biblatexoptions:
  - sortcites
csl: csl/apa.csl
link-citation: yes
mainfont: Arial
fontsize: 11pt
---

```{r setup, include = FALSE}
needed_packages <- c("wjake", "here", "fs", "glue", "pluralize", "english",
                     "knitr", "kableExtra", "ggplot2", "lubridate",
                     "showtext", "conflicted")
load_packages <- function(x) {
  if (!(x %in% installed.packages())) {
    if (x == "wjake") {
      remotes::install_github("wjakethompson/wjake", dependencies = TRUE)
    } else {
      install.packages(x, repos = "https://cran.rstudio.com/")
    }
  }
  suppressPackageStartupMessages(require(x, character.only = TRUE))
}
vapply(needed_packages, load_packages, logical(1))

conflict_prefer("filter", "dplyr")
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("set_theme", "wjake")

complete_date <- ymd(rmarkdown::metadata$author$complete_date)

showtext_auto()
showtext_opts(dpi = 320)

options(knitr.kable.NA = "")
set_theme(base_family = "Source Sans Pro", plot_margin = margin(0, 10, 0, 10))
```

Introductory paragraph.

# Analyses to be Conducted

Summary of analyses.

# Timeline and Deliverables

I currently estimate approximately `r round((complete_date - today()) / dweeks(1), digits = 0)` weeks to complete the analyses outlined above and develop a report of the findings. I can begin this work upon approval of this estimate with an estimated completion date of `r glue("{month(complete_date, label = TRUE, abbr = FALSE)} {day(complete_date)}, {year(complete_date)}")`. Upon completion of the report, a private GitHub repository will be shared with the project staff. Alternatively, a compressed zip folder of the GitHub repository can also be provided upon request. The repository will contain the following:

* The original and other associated files that were provided by the project staff
* R scripts that can be used to replicate all analyses
* Data visualizations to illustrate the results of the analyses
* The completed report

A PDF of the final report will also be provided by email to project staff.

# Estimated Cost

The cost estimate for the above outlined activities are based on the expected hours for each activity. All work is quoted at a consulting rate of \$`r rmarkdown::metadata$author$fee`/hour.\
\

```{r cost-estimate}
est_time <- tribble(
  ~task,                                                          ~hours,
  "Report Development",                                               5L
)

est_time %>%
  kbl(align = c("l", "c"), booktabs = TRUE, linesep = "", escape = FALSE,
      col.names = c("Task", "Hours")) %>%
  kable_styling(latex_options = "HOLD_position", full_width = TRUE) %>%
  column_spec(1, width = "40em") %>%
  row_spec(0, align = "c")
```
\
The total estimated time for this project is `r sum(est_time$hours)` hours. At \$`r rmarkdown::metadata$author$fee`/hour, the total cost is estimated to be \$`r sum(est_time$hours) * rmarkdown::metadata$author$fee`. In addition, I would expect to be included on any publications or conference presentations that utilize this work.

If any clarifications or modifications are needed for this estimate, please feel free to contact wjakethompson\@gmail.com.\
\
Thank you,\
\
\
W. Jake Thompson, Ph.D.

\newpage

# References

```{r write-packages, include = FALSE}
if (!file.exists("bib/packages.bib")) file.create("bib/packages.bib")
suppressWarnings(
  knitr::write_bib(c(.packages()), "bib/packages.bib")
)
```

\printbibliography[heading=none]

\setlength{\parindent}{15pt}
\setlength{\leftskip}{0pt}
